---
title: "521 Lab 3: Cars Analysis"
subtitle: "Exploring Speed vs Stopping Distance"
author: "Yuting, Junli, Komalpreet, Audrija"
institute: "UBC"
date: "2025/9/17"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


```{r setup, include=FALSE}
library(ggplot2)
options(htmltools.dir.version = FALSE)
```

# Slide 1 — Introduction

We'll explore the **relationship between car speed and stopping distance**.

**Goals:**
- Summarize the dataset with key statistics
- Visualize trends with plots

**Dataset:** `cars` (speed and stopping distance)

---

# Slide 2 — Summary Statistics

```{r}
# Simple statistics for cars dataset
x <- cars$speed
y <- cars$dist

summary_stats <- data.frame(
  Variable = c("Speed", "Distance"),
  Mean = c(mean(x), mean(y)),
  SD = c(sd(x), sd(y)),
  Min = c(min(x), min(y)),
  Max = c(max(x), max(y))
)
summary_stats
```
---

# Slide 3 — Speed vs Stopping Distance Plot
  
```{r, fig.height=4}
ggplot(cars, aes(x = speed, y = dist)) +
  geom_point(color = "blue", size = 3) +
  geom_smooth(method = "lm", color = "red", linetype = "dashed") +
  labs(title = "Car Speed vs Stopping Distance",
       x = "Speed (mph)", y = "Stopping Distance (ft)") +
  theme_minimal(base_size = 16)
```
---

# Slide 4 — Conclusion

**Summary:**
- Speed affects stopping distance significantly.

**Key Takeaway:**
- Safety depends on speed — faster vehicles require more distance to stop.

**Thank you!** Questions welcome.